\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-08-19 NAR_DRAFT.tex
fix captions for supplement figures

\begin{figure}[b]
  \begin{center}
  \includegraphics{figures/fig_wgs.pdf}
  \end{center}
  \caption{Model performance on 100X simulated whole genome.
  \textbf{(a)} Precision recall curves and \textbf{(c)} Reciever operating characteristic curves for 3 mutation signatures.
  Distribution of estimated true positive probabilities for true positive (top) and true negative (bottom) variants for \textbf{b)} the MuTect model and \textbf{d)} the BATCAVE model.
  A perfectly calibrated model would generate the diagonal line.}
\label{NAR-wgs_fig}
\end{figure}

\clearpage
\begin{figure}
  \begin{center}
  \includegraphics{figures/ppv_wgs.pdf}
  \end{center}
  \caption{Model performance on 500X simulated whole exome. 
  Positive predictive values vs. Recall for three different probability cutoffs. 
  Note the restricted axes to improve readability of points.}
\label{NAR-ppv_wgs_fig}
\end{figure}

>>>>

\begin{figure}[b]
  \begin{center}
  \includegraphics{figures/fig_wgs.pdf}
  \end{center}
  \caption{Model performance on 100X simulated whole genome.
  \textbf{(a)} Precision recall curves and \textbf{(c)} Reciever operating characteristic curves for 3 mutation signatures.
  Distribution of estimated true positive probabilities for true positive  variants for \textbf{b)} the MuTect model and \textbf{d)} the BATCAVE model.
  A perfectly calibrated model would generate the diagonal line.}
\label{NAR-wgs_fig}
\end{figure}

\clearpage
\begin{figure}
  \begin{center}
  \includegraphics{figures/ppv_wgs.pdf}
  \end{center}
  \caption{Model performance on 100X simulated whole genome. 
  Positive predictive values vs. Recall for three different probability cutoffs. 
  Note the restricted axes to improve readability of points.}
\label{NAR-ppv_wgs_fig}
\end{figure}
